Comparative study of requantization of time-dependent mean-field for pairing dynamics

### 2017-09-29 draft1.1.tex
test
added some figures, changed 5.C a little

%aaa
\usepackage{comment}
%\usepackage[dvips]{graphicx}
%\usepackage{amsmath,amssymb}
%\usepackage{mathrsfs}
%\usepackage{txfonts}
\usepackage{braket}
%\usepackage{latexsym}
%\usepackage{ascmac}
%\usepackage{fancybox}
%\usepackage{type1cm}
\usepackage{cases}
\usepackage{caption}
\usepackage[top=25truemm,bottom=20truemm,left=20truemm,right=20truemm]{geometry}

@@

In the superfluid phase, the energy minimization always lead to $\phi=0$.
Although the global gauge angle $\Phi$ is arbitrary,
the gap parameter is usually taken as real value ($\Phi=0$).
\begin{align}
\Delta(j,J) = g\braket{Z_0|\hat{S}_-|Z_0} %= g\sum_{k>0} u_kv_k \nonumber \\
	= g\sum_{l=1}^2 S_l\sqrt{1-q_l^2} . % = \Delta(\pi) .
 \label{Delta_BCS}
\end{align}
The relation between $j$ and $\Delta$ 
and that between $j$ and $E=\cal{H}(\phi=0,j;J)$
are shown for $\Omega=8$
in Figs. \ref{fig:p_Delta1} ($N=8$) and \ref{p_Delta2} ($N=16$).
%These results correspond to the system in Section 4.2. 
The gap $\Delta$ is largest at $j=0$ (equal filling in both levels),
and smallest at end points of $j$.
The constrained minimization with respect to $\Delta$ cannot 
produce the states corresponding to $j>0$.
Apparently, we cannot map the entire region of $j$ to $\Delta$,
since there is no one-to-one correspondence between $j$ and $\Delta$.

If the system has a deep potential at $j<0$ to prevent the wave function
from spreading toward the region of $j<0$,
we may justify the use of $\Delta$ as a coordinate in
the collective model.
For very large $\Omega$, this is the case.
However, for $\Omega=8$, the treatment can be justified only for
a very limited region of $x$, namely in the weak pairing limit.
For instance, we show the potential energy curves as functions of $\Delta$
in Fig.~\ref{fig:Delta_E} for the $N=16$ case.
In the weak pairing case ($x=0.5$),
assuming the Neumann boundary condition at $\Delta=0$,
we may obtain the colletive wave functions up to the third excited states.
On the other hand, in the strong pairing case ($x=3.2$), 
even the ground state may not be bound in the region of $j<0$.

@@

\begin{figure}[htbp]
 \begin{center}
%  \includegraphics[width=45mm,angle=-90]{images/N8p_Delta.eps}
 \end{center}
 \caption{Pairing gap $\Delta$ in (\ref{Delta_BCS}) as a function of $\pi$ with various pairing strength in $N=8$ system.}
 \label{fig:p_Delta1}
\end{figure}

\begin{figure}[htbp]
 \begin{center}
%  \includegraphics[width=45mm,angle=-90]{images/N16p_Delta.eps}
 \end{center}
 \caption{Pairing gap $\Delta$ in (\ref{Delta_BCS}) as a function of $\pi$ with various pairing strength in $N=16$ system.}
 \label{fig:p_Delta2}
\end{figure}

>>>>

%aaa
\usepackage{comment}
\usepackage[dvips]{graphicx}
%\usepackage{amsmath,amssymb}
%\usepackage{mathrsfs}
%\usepackage{txfonts}
\usepackage{braket}
%\usepackage{latexsym}
%\usepackage{ascmac}
%\usepackage{fancybox}
%\usepackage{type1cm}
\usepackage{cases}
\usepackage{caption}
\usepackage[top=25truemm,bottom=20truemm,left=20truemm,right=20truemm]{geometry}

@@

In the superfluid phase, the energy minimization always lead to $\phi=0$.
Although the global gauge angle $\Phi$ is arbitrary,
the deformation parameter $\alpha$ in gauge space is usually taken as real value ($\Phi=0$).
\begin{align}
\alpha(j,J) = \braket{Z_0|\hat{S}_-|Z_0} %= g\sum_{k>0} u_kv_k \nonumber \\
	= \sum_{l=1}^2 S_l\sqrt{1-q_l^2} . % = \Delta(\pi) .
 \label{Delta_BCS}
\end{align}
The relation between $j$ and $\alpha$ 
and that between $j$ and $E=\mathcal{H}(\phi=0,j;J)$
are shown for $\Omega=8$
in Figs. \ref{fig:p_Delta1} ($N=8$) and \ref{p_Delta2} ($N=16$).
%These results correspond to the system in Section 4.2. 
The deformation parameter $\alpha$ is largest at $j=0$ (equal filling in both levels),
and smallest at end points of $j$.
The constrained minimization with respect to $\alpha$ cannot 
produce the states corresponding to $j>0$.
Apparently, we cannot map the entire region of $j$ to $\alpha$,
since there is no one-to-one correspondence between $j$ and $\alpha$.

If the system has a deep potential at $j<0$ to prevent the wave function
from spreading toward the region of $j<0$,
we may justify the use of $\alpha$ as a coordinate in
the collective model.
For very large $\Omega$, this is the case.
However, for $\Omega=8$, the treatment can be justified only for
a very limited region of $x$, namely in the weak pairing limit.
For instance, we show the potential energy curves as functions of $\alpha$
in Fig.~\ref{fig:Delta_E} for the $N=16$ case.
In the weak pairing case ($x=0.5$),
assuming the Neumann boundary condition at $\alpha=0$,
we may obtain the colletive wave functions up to the third excited states.
On the other hand, in the strong pairing case ($x=3.2$), 
even the ground state may not be bound in the region of $j<0$.

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=45mm,angle=-90]{images/N8p_Delta.eps}
 \end{center}
 \caption{Pairing gap $\Delta$ in (\ref{Delta_BCS}) as a function of $\pi$ with various pairing strength in $N=8$ system.}
 \label{fig:p_Delta1}
\end{figure}

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=45mm,angle=-90]{images/N16p_Delta.eps}
 \end{center}
 \caption{Pairing gap $\Delta$ in (\ref{Delta_BCS}) as a function of $\pi$ with various pairing strength in $N=16$ system.}
 \label{fig:p_Delta2}
\end{figure}
